Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-18 manuscript/supplemental_material.Rnw
move per-species go analyses up to match the paper order
remove lineage table

@@

\begin{table}[hb]
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{the rodentia order}{all other species}}
\label{tab:rodentia_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<lau.lineage.specific,echo=FALSE,results="asis">>=
lau.all.lin.spec <- placenta.lineage.specific.table("lau.all")
setkey(lau.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{the laurasiatheria
    superorder}{all other species}}
\label{tab:laurasiatheria_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<eua.lau.lineage.specific,echo=FALSE,results="asis">>=
eua.lau.lin.spec <- placenta.lineage.specific.table("eua.lau")
setkey(eua.lau.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{ the euarchontoglires superorder}{ the laurasiatherian superorder}}
\label{tab:laurasiatheria_euarchontoglires_lineage_specific}
\end{table}

>>>>

\section{Per-Species GSEA}

@@
